Supporting Information

### 2022-08-01 Manuscript/Main_text/Main_text_Journal_of_Animal_Ecol.Rmd
git push

First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies. For this, we used the trait dataset collated in @lanuza2021 that comprised a total of 1506 species including the 503 species considered in this study (Table S2). This dataset consisted of 8 floral, 4 reproductive biology and 3 plant morphology traits excluding traits with high percentage of missing values (over 30$\%$; Table S3). We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014]. To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971]. For this, we used the function _gowdis_ with method _ward.D2_ from the _FD_ package version _1.0-12_ [@laliberte2014]. Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the _maptree_ package version _1.4-7_ [@white2009].

@@

We calculated which plant and floral visitor groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts. To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class (i.e., 2, 3, 4 or 5 species motifs). Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with subgraph frequencies. To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network. We used the group identifier as an explanatory variable and the study identifiers as a random intercept. Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level. Finally, we visualized with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016] over- and under-representation of plant and floral visitor groups on the different subgraph positions.

To understand if the different plant and floral visitor groups are associated with subgraph positions that represent different network roles, we characterized the roles of each subgraph position for plant and floral visitor groups in terms of their specialisation and number of indirect interactions. To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph. Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph). Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position as $n_i=z_i-k_i-1$, where $z_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position. Thus, we considered all possible indirect interactions for each position. Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above). For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables. Further, we considered as random factor subgraph position nested within study system. All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0.

@@

The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S4 and S5). The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing. The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers. The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules. The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant. Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.

@@

For both floral visitor and plant groups we found over- and under-representation on different subgraph positions that implied different ecological roles. First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig. S6 A). Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig. S6 B). Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig. S7 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks. For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig. S7 B). When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S8 and S9).

>>>>

First, plant species were grouped through hierarchical clustering into the optimal number of functional groups that summarized the main plant reproductive strategies. For this, we used the plant trait dataset compiled in @lanuza2021 that consisted also of plant species that belonged to the same plant-pollinator networks plus some additional meta-networks not considered here in order to use just networks with similar sampling effort (e.g., unique location and flowering season). This dataset comprised a total of 1506 plant species including the 503 species considered in this study (Table S2). Because most of these plant species are likely to benefit from animal pollination, we used reproductive traits relevant to understand the different plant reproductive strategies and their interactions with pollinators. After excluding traits with high percentage of missing values (over 30$\%$), we ended up with 8 floral, 3 reproductive biology and 3 plant morphology traits (see Table S3 for a list of all traits). Floral traits included those associated with the size, form and number of floral organs (e.g., style length or ovule number). Reproductive biology traits described the reproductive system of the plant (i.e., the breeding, mating and compatibility system) and plant morphology traits were associated with the size and form of the plant (i.e., plant height, lifespan and life form). After an extensive search for each plant species on several different resources (e.g., plant databases, online floras, books, journals and images), over 80% of the cells of the whole dataset were filled. Thus, to avoid the loss of species with trait missing values, missing trait data was imputed as detailed in @lanuza2021.

We opted to calculate the plant functional groups within a larger set of species because of the higher accuracy when delimiting functional groups with that many variables and species [@dolnicar2014]. To feed the clustering analysis, we calculated the distance between the different qualitative and scaled quantitative variables with Gower distance [@gower1971]. For this, we used the function _gowdis_ with method _ward.D2_ from the _FD_ package version _1.0-12_ [@laliberte2014]. Finally, we conducted hierarchical clustering with the function _hclust_ from the _R_ stats package version _4.0.5_ and calculated the optimal number of clusters with the function _kgs_ from the _maptree_ package version _1.4-7_ [@white2009].

@@

We calculated which plant and floral visitor groups were over- or under-represented in the different subgraph positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts. To estimate the position frequencies of each plant and floral visitor group in a given network, we added the frequencies of those species that belong to the same group, and then, we normalised the resulting frequencies by dividing them by the total number of times that a corresponding group appears in any position within the same subgraph size class (i.e., 2, 3, 4 or 5 species motifs). Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with subgraph frequencies. To outline the general patterns of position frequencies across networks and groups, we fit a LMM per subgraph position, where the response variable was the observed position percentile per network. We used the group identifier as an explanatory variable and the study identifiers as a random intercept. Hence, we assessed the average subgraph frequency per species group, after controlling for the variation at the study level. Finally, we visualized over- and under-representation of plant and floral visitor groups on the different subgraph positions with the help of the _ComplexHeatmap_ package version _2.6.2_ [@gu2016].

To understand if the different plant and floral visitor groups are associated with subgraph positions that represent different network roles, we characterized the roles of each subgraph position for plant and floral visitor groups in terms of their specialisation and number of indirect interactions. To that end, we calculated the specificity of each subgraph position following @poisot2015 as $s_i = (L - l_i) / (L - 1)$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given subgraph. Values of the vector $si$, range between 1, complete specialisation (1 partner within the subgraph) and 0 complete generalism (all possible partners within the subgraph). Then, because all nodes within a motif are connected, we calculated the number of indirect interactions ($n_i$) for each motif position as $n_i=z_i-k_i-1$, where $z_i$ is the total number of nodes in a given motif, and $k_i$ represents the degree of the corresponding motif position, that is, the total number of links connected to such position. Thus, we considered all possible indirect interactions for each position. Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and subgraph position (see paragraph above). For this, we fitted a LMM model with the help again of the _lme4_ package where we considered specialization and number of indirect interactions as response variables with the interaction by plant and floral visitor group for both response variables. Further, we considered as random factor subgraph position nested within study system. All model diagnostics were conducted with the help of the _Dharma_ package [@hartig2017] version _0.3.3.0_ and model outputs were visualized with the _visreg_ package [@breheny2020] version 2.7.0. Finally, to verify that different levels of richness across plant and floral visitor groups are not driving the overall results of indirect interactions and specialization, we conducted the analogous analyses for 1000 random samples of the 60% of the networks. We found consistent results that indicate that different richness across groups have negligible effects on the overall patterns (see Figs S4 and S5).

@@

The hierarchical cluster analysis divided the dataset into five different groups with different and overlapping characteristics (Figs S6 and S7). The first group referred to as 'selfing herbs' consisted of herbs with hermaphroditic flowers with high levels of autonomous selfing. The second group named 'small outcrossing perennials' had small perennial species with a mix of life forms (i.e., trees shrubs and herbs) with outcrossing hermaphroditic flowers. The third group referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules. The fourth group named 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems, small flowers and the highest numbers of flowers and inflorescences per plant. Finally, the fifth group named 'short-lived outcrossers with long zygomorphic flowers' consisted of small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.

@@

For both floral visitor and plant groups we found over- and under-representation on different subgraph positions that implied different ecological roles. First, for floral visitors, we found that bees were less frequent on subgraph positions that involved specialization (i.e., lower specificity values) while the rest of taxonomic groups (non-syrphid Diptera, syrphids, Lepidoptera, Coleoptera and non-bee Hymenoptera) were infrequent in generalised subgraph positions with low number of indirect interactions (Fig. S8 A). Although plants did not show differences with null models on their frequencies, all plant but tall plants with small unisexual flowers showed a slight tendency to be over-represented on specialised subgraph positions (Fig. S8 B). Second, regarding the number of indirect interactions, bees were over-represented in subgraph positions with low number of indirect interactions (Fig. S9 A) and the rest of floral visitor groups showed no differences across positions in comparison with simulated networks. For plants, all groups showed a slight trend to be over-represented on subgraph positions with higher number of indirect interactions (Fig. S9 B). When we further explore the observed frequencies by number of indirect interactions for floral visitor and plant groups, we found that both bees and tall plants with small unisexual flowers were the only groups with high frequencies on subgraph positions associated with low number interactions in comparison with the other floral visitor and plant groups (Figs S10 and S11).

### 2022-08-01 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
adding Nacho's edits
git push

**The non-random assembly of functional motifs in plant-pollinator networks**

@@

Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")

T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))

@@

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Plant functional group composition separated in qualitative and quantitative variables. Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group. Plot B) shows the radar plot of the different quantitative variables standardise on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group. Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S5.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5). The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters. The rest of species labels are omitted for visualization purposes (N = 982)."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

>>>>

**The non-random assembly of indirect interactions in plant-pollinator networks**

@@

Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Compatibility system", "Breeding system", "", "")

T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic",  "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious","", ""),align = c("l"))

@@

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "", "")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Association between the percentile (frequency comparison between empirical and simulated networks) and specialization of the different plant and floral visitor groups on the distinct motif positions for 1000 random sets that contain the 60% of the whole set of networks each. Black lines represent the mean percentile values of random samples and the continuous red line indicates the mean percentile values for the whole set of networks. Grey areas show the 95% confidence intervals for random samples, whereas those for the whole set of networks are displayed by using red dashed lines. Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks."}

library(tidyverse)

# Load data for all datasets------------------------

percentage_studies_load <- 1.0
repetitions_load <- 1

file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

# Load data for a fraction of the total datasets-----------------

percentage_studies_load <- .60
repetitions_load <- 100

file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

pollinator_names <- list(
  '1'="Bee",
  '2'="Coleoptera",
  '3'="Lepidoptera",
  '4'="Non-bee-Hymenoptera",
  '5'="Non-syrphids-diptera",
  '6'="Syrphids"
)

plant_names <- list(
  '1'="Selfing herbs",
  '2'="Small outcrossing perennials",
  '3'="Self-incompatible perennials\nwith large flowers",
  '4'="Tall plants with small\nunisexual flowers",
  '5'="Short-lived outcrossers with\nlong zygomorphic flowers")

pollinator_labeller <- function(variable,value){
  return(pollinator_names[value])
}

plant_labeller <- function(variable,value){
  return(plant_names[value])
}

final_pollinator_sp_plot <- ggplot(shade_data_pollinator_sp_plot)+
  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
  facet_grid( ~ PANEL, labeller=pollinator_labeller)+
  geom_line(data = mean_line_data_pollinator_sp_plot, 
            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
  geom_line(data = shade_data_pollinator_sp_plot_all,
              aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
  geom_line(data = shade_data_pollinator_sp_plot_all,
            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
  geom_line(data = mean_line_data_pollinator_sp_plot_all, 
            aes(x = x, y = y, color ="red"), size = 1.2)+
  theme_bw()+
  ggtitle("Floral visitors") +
  labs(y="Percentile", x =NULL)+
  theme(legend.position = "none")

final_plant_sp_plot <- ggplot(shade_data_plant_sp_plot)+
  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
  facet_grid( ~ PANEL, labeller=plant_labeller)+
  geom_line(data = mean_line_data_plant_sp_plot, 
            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
  geom_line(data = shade_data_plant_sp_plot_all,
            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
  geom_line(data = shade_data_plant_sp_plot_all,
            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
  geom_line(data = mean_line_data_plant_sp_plot_all, 
            aes(x = x, y = y, color ="red"), size = 1.2)+
  theme_bw()+
  ggtitle("Plants")+
  labs(x = "Specialization", y="Percentile")+
  theme(legend.position = "none")

library(patchwork)

final_pollinator_sp_plot/final_plant_sp_plot & theme(axis.text=element_text(size=10),
                                                    axis.title=element_text(size=16)) & 
  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S5.** Association between the percentile (frequency comparison between empirical and simulated networks) and number of indirect interactions of the different plant and floral visitor groups on the distinct motif positions for 1000 random sets that contain the 60% of the whole set of networks each. Black lines represent the mean percentile values of random samples and the continuous red line indicates the mean percentile values for the whole set of networks. Grey areas show the 95% confidence intervals for random samples, whereas those for the whole set of networks are displayed by using red dashed lines. Note that percentiles above 0.75 indicate over-representation and those below 0.25 under-representation in the comparison between empirical and simulated networks. "}

library(tidyverse)

# Load data for all datasets------------------------

percentage_studies_load <- 1.0
repetitions_load <- 1

file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_sp_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_int_plot_all <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

# Load data for a fraction of the total datasets-----------------

percentage_studies_load <- .60
repetitions_load <- 100

file_suffix <- paste0("pollinator_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("pollinator_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_pollinator_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_sp_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_sp_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

file_suffix <- paste0("plant_int_plot_",repetitions_load,"_repetitions_",
                      round(100*percentage_studies_load),"_percent.csv")

shade_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/shade_data_",file_suffix))
mean_line_data_plant_int_plot <- read_csv(paste0("../../Data/Csv/mean_line_data_",file_suffix))

pollinator_names <- list(
  '1'="Bee",
  '2'="Coleoptera",
  '3'="Lepidoptera",
  '4'="Non-bee-Hymenoptera",
  '5'="Non-syrphids-diptera",
  '6'="Syrphids"
)

plant_names <- list(
  '1'="Selfing herbs",
  '2'="Small outcrossing perennials",
  '3'="Self-incompatible perennials\nwith large flowers",
  '4'="Tall plants with small\nunisexual flowers",
  '5'="Short-lived outcrossers with\nlong zygomorphic flowers")

pollinator_labeller <- function(variable,value){
  return(pollinator_names[value])
}

plant_labeller <- function(variable,value){
  return(plant_names[value])
}

final_pollinator_int_plot <- ggplot(shade_data_pollinator_int_plot)+
  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
  facet_grid( ~ PANEL, labeller=pollinator_labeller)+
  geom_line(data = mean_line_data_pollinator_int_plot, 
            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
  geom_line(data = shade_data_pollinator_int_plot_all,
            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
  geom_line(data = shade_data_pollinator_int_plot_all,
            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
  geom_line(data = mean_line_data_pollinator_int_plot_all, 
            aes(x = x, y = y, color ="red"), size = 1.2)+
  theme_bw()+
  ggtitle("Floral visitors") +
  labs(y="Percentile", x =NULL)+
  theme(legend.position = "none")

final_plant_int_plot <- ggplot(shade_data_plant_int_plot)+
  geom_ribbon(aes(x=x, ymax=ymax, ymin= ymin, fil = as.factor(repetition)), alpha=1/repetitions_load)+
  facet_grid( ~ PANEL, labeller=plant_labeller)+
  geom_line(data = mean_line_data_plant_int_plot, 
            aes(x = x, y = y, co = as.factor(repetition)), alpha=0.5)+
  geom_line(data = shade_data_plant_int_plot_all,
            aes(x=x, y=ymax, color ="red"), size = 1.2,linetype = "dashed")+
  geom_line(data = shade_data_plant_int_plot_all,
            aes(x=x, y= ymin, color ="red"), size = 1.2, linetype = "dashed")+
  geom_line(data = mean_line_data_plant_int_plot_all, 
            aes(x = x, y = y, color ="red"), size = 1.2)+
  theme_bw()+
  ggtitle("Plants")+
  labs(y="Percentile", x ="Number of indirect interactions")+
  theme(legend.position = "none")

library(patchwork)

final_pollinator_int_plot/final_plant_int_plot & theme(axis.text=element_text(size=10),
                                                       axis.title=element_text(size=16)) & 
  plot_annotation(tag_levels = c('A'),  tag_suffix = ')') &  theme(plot.tag = element_text(size = 22))

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S6.** Plant functional group composition separated in qualitative and quantitative variables. Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group. Plot B) shows the radar plot of the different quantitative variables standardise on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group. Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="**Figure S7.** Hierarchical clustering dendrogram with the branches coloured by the optimal number of clusters (5). The labels of the subgroup of species (N = 524) used in this study are coloured in black in order to show the evenness of the distribution of the species across clusters. The rest of species labels are omitted for visualization purposes (N = 982)."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S8.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S9.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S10.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S11.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}
